Robust Trajectory Optimization on a Quantum System

### 2021-01-26 paper/0abstract.tex
revised based on dave comments

%% TITLE
\title{Robust Quantum Optimal Control}

@@

%% ABSTRACT
\begin{abstract}
  The ability to engineer high-fidelity gates on quantum processors in the presence of
  systematic errors remains the primary challenge requisite to achieving quantum advantage.
  Quantum optimal control methods have proven effective in experimentally
  realizing high-fidelity gates, but they require exquisite calibration to be performant.
  We apply robust trajectory optimization techniques to suppress gate errors arising from system
  parameter uncertainty.
  We propose a method that takes advantage of uncertain parameter
  derivative information while maintaining
  computational efficiency by transforming high-order differential equations to coupled,
  first-order ODEs.
  Additionally, the effect of depolarization on a gate is most accurately modeled by
  integrating the Lindblad master equation,
  which is computationally expensive.
  We propose a computationally efficient model
  and utilize time-optimal control to achieve high fidelity gates in the presence of depolarization.
  We apply these techniques to a fluxonium qubit with realistic
  parameters and constraints,
  achieving orders of magnitude gate-error reductions from our baseline gate set in simulations.
\end{abstract}

>>>>

%% TITLE
\title{Robust Trajectory Optimization on a Quantum System}

@@

%% ABSTRACT
\begin{abstract}
  The ability to engineer high-fidelity gates on quantum processors in the presence of
  systematic errors remains the primary challenge requisite to achieving quantum advantage.
  Quantum optimal control methods have proven effective in experimentally
  realizing high-fidelity gates, but they require exquisite calibration to be performant.
  We apply robust trajectory optimization techniques to suppress gate errors arising from system
  parameter uncertainty.
  We propose a method that takes advantage of uncertain parameter
  derivative information while maintaining
  computational efficiency by transforming high-order differential equations to coupled,
  first-order ODEs.
  Additionally, the effect of depolarization on a gate is most accurately modeled by
  integrating the Lindblad master equation,
  which is computationally expensive.
  We propose a computationally efficient model
  and utilize time-optimal control to achieve high fidelity gates in the presence of depolarization.
  We apply these techniques to a fluxonium qubit and suppress
  simulated gate errors due to parameter uncertainty below $10^{-7}$ for
  static parameter deviations on the order of $1\%$.
\end{abstract}

### 2021-01-26 paper/1introduction.tex
revised based on dave comments

\section{Introduction}
Quantum optimal control (QOC) is a class of optimization
algorithms for accurately and efficiently manipulating quantum systems.
Early techniques were proposed for nuclear magnetic resonance experiments
\cite{vandersypen2005nmr, kehlet2004improving, khaneja2005optimal,
  maximov2008optimal, nielsen2010optimal, skinner2003application, tosner2009optimal},
and applications now include superconducting circuits \cite{abdelhafez2020universal,
  chakram2020multimode, fisher2010optimal, gokhale2019partial,
  huang2020engineering, leng2019robust, leung2017speedup, li2020fast,
  xu2020nonadiabatic},
neutral atoms and ions \cite{brouzos2015quantum,
  de2008optimal, goerz2011quantum, guo2019high, jensen2019time,
  larrouy2020fast, omran2019generation, rosi2013fast, sorensen2019qengine,
  treutlein2006microwave, van2016optimal},
nitrogen-vacancy centers in diamond \cite{chou2015optimal,
  dolde2014high, geng2016experimental,
  nobauer2015smooth, poggiali2018optimal, rembold2020introduction, tian2019optimal},
and Bose-Einstein condensates \cite{amri2019optimal, sorensen2018quantum}.
For quantum computation,
optimal control is employed to achieve high-fidelity gates
while adhering to experimental constraints.
Experimental errors may cause the system to deviate
from the model used in optimization, leading
to poor experimental performance.
Robust control improves upon
standard optimal control by encoding
model parameter uncertainties
in optimization objectives, yielding performance
guarantees over a range of parameter values \cite{Zhou97,Morimoto00,Manchester18}.
We adapt robust control techniques from the robotics community to mitigate
parameter uncertainty errors for
a superconducting fluxonium qubit.

QOC has had tremendous success in
engineering high-fidelity quantum gates \cite{
  chou2015optimal, dolde2014high, egger2013optimized, egger2014adaptive,
  grace2007optimal, heeres2017implementing, huang2014optimal,
  kelly2014optimal, leng2019robust, liebermann2016optimal,
  nebendahl2009optimal, rebentrost2009optimal, rebentrost2009optimal2,
  spiteri2018quantum, sporl2007optimal}. 
However, the system often
deviates from the model used in optimization
due to experimental errors such as parameter drift, noise, finite control 
resolution, and decoherence. Multiple techniques have been
developed to address this shortcoming.
Analytically-derived control pulses that
mitigate parameter uncertainty errors include
composite pulses \cite{cummins2000use, cummins2003tackling,
  kupce1995stretched, merrill2014progress},
pulses designed by considering dynamic and geometric phases
\cite{han2020experimental, xu2020nonadiabatic}, and
pulses obtained with the DRAG scheme \cite{motzoi2009simple}.
To suppress decoherence, Floquet techniques have been employed
\cite{huang2020engineering, mundada2020floquet}.
Numerical schemes to mitigate parameter uncertainty errors
include closed-loop methods \cite{egger2014adaptive, feng2018gradient,
  wittler2020integrated} and open-loop methods \cite{
  allen2019robust, carvalho2020error, reinhold2019controlling,
  rembold2020introduction, kosut2013robust}.
To model decoherence, numerical techniques typically employ
master equations \cite{rembold2020introduction, schulteherbruggen2011optimal} or
Monte Carlo-style quantum trajectories \cite{abdelhafez2019gradient}.

In this work, we study three robust control techniques that
make the system's quantum state trajectory less sensitive
to static and time-dependent parameter uncertainty:
\begin{enumerate}
  \item A sampling method, similar to the work of \cite{allen2019robust,
    carvalho2020error, khaneja2005optimal, reinhold2019controlling, rembold2020introduction}.
  \item An unscented sampling method adapted from the unscented transform used in
    state estimation \cite{howell2020direct, julier2004unscented,
      lee2013sigma, manchester2016derivative}.
  \item A derivative method, which penalizes the sensitivity of the quantum state trajectory
    to uncertain parameters.
\end{enumerate}
We apply these techniques to the fluxonium qubit presented in \cite{zhang2020universal}.
We also show that QOC can solve important problems associated with
fluxonium-based qubits: mitigating
depolarization by taking advantage of the $T_{1}$-dependence of the controls
and synchronizing qubits with distinct frequencies
by performing phase gates in arbitrary times.
To mitigate depolarization,
we perform time-optimal control and
employ an efficient depolarization model that 
is significantly less expensive to compute than integrating a master equation.
Leveraging recent advances in trajectory optimization within the field of robotics, we
solve these optimization problems using ALTRO (Augmented Lagrangian TRajectory Optimizer)
\cite{howell2019altro}, which uses the iterative linear quadratic regulator (iLQR) method
\cite{Li2004a} within an augmented Lagrangian framework \cite{lantoine2012hybrid,
  plancher2017constrained}
to handle nonlinear equality and inequality constraints at 
each time step.

This paper is organized as follows.
First, we reintroduce ALTRO in the context of QOC
in Section \ref{sec:background}.
We describe realistic constraints for operating the fluxonium and
define the associated QOC problem in Section \ref{sec:fluxonium}.
Then, we outline a method for making the optimization aware of depolarization
in Section \ref{sec:longitude}. Next, we outline three techniques for achieving
robustness to static parameter uncertainties in Section \ref{sec:static}. We
adapt the same techniques to mitigate 1/$f$ flux noise
in Section \ref{sec:stochastic}.

>>>>

\section{Introduction}
Quantum optimal control (QOC) is a class of optimization
algorithms for accurately and efficiently manipulating quantum systems.
Early techniques were proposed for nuclear magnetic resonance experiments
\cite{vandersypen2005nmr, kehlet2004improving, khaneja2005optimal,
  maximov2008optimal, nielsen2010optimal, skinner2003application, tosner2009optimal},
and applications now include superconducting circuits \cite{abdelhafez2020universal,
  chakram2020multimode, fisher2010optimal, gokhale2019partial,
  leng2019robust, leung2017speedup, li2020fast},
neutral atoms and ions \cite{brouzos2015quantum,
  de2008optimal, goerz2011quantum, guo2019high, jensen2019time,
  larrouy2020fast, omran2019generation, rosi2013fast, sorensen2019qengine,
  treutlein2006microwave, van2016optimal},
nitrogen-vacancy centers in diamond \cite{chou2015optimal,
  dolde2014high, geng2016experimental,
  nobauer2015smooth, poggiali2018optimal, rembold2020introduction, tian2019optimal},
and Bose-Einstein condensates \cite{amri2019optimal, sorensen2018quantum}.
In the context of quantum computation,
optimal control is employed to achieve high-fidelity gates
while adhering to experimental constraints.
Experimental errors such as parameter drift, noise, and
finite control resolution cause the system to deviate
from the model used in optimization, leading
to poor experimental performance.
Robust control improves upon
standard optimal control by encoding
model parameter uncertainties
in optimization objectives, yielding performance
guarantees over a range of parameter values \cite{Zhou97,Morimoto00,Manchester18}.
We adapt robust control techniques from the robotics community to mitigate
parameter uncertainty errors for
a superconducting fluxonium qubit.

Analytically-dervied control pulses that mitigate parameter uncertainty
errors include composite pulses \cite{cummins2000use, cummins2003tackling,
  kupce1995stretched, merrill2014progress},
pulses designed by considering dynamic and geometric phases
\cite{han2020experimental, xu2020nonadiabatic}, and
pulses obtained with the DRAG scheme \cite{motzoi2009simple}.
These techniques are not amenable to arbitrary experimental constraints,
so recent work has sought to achieve robustness in quantum optimal
control frameworks using closed-loop methods \cite{egger2014adaptive, feng2018gradient,
  wittler2020integrated} and open-loop methods \cite{
  allen2019robust, carvalho2020error, reinhold2019controlling,
  rembold2020introduction, kosut2013robust}.

In this work, we study three robust control techniques that
make the system's quantum state trajectory less sensitive
to static and time-dependent parameter uncertainty:
\begin{enumerate}
\item A sampling method, similar to the work of \cite{allen2019robust,
  ball2020software, carvalho2020error, khaneja2005optimal,
  reinhold2019controlling, rembold2020introduction}.
  \item An unscented sampling method adapted from the unscented transform used in
    state estimation \cite{howell2020direct, julier2004unscented,
      lee2013sigma, thangavel2020robust}.
  \item A derivative method, which penalizes the sensitivity of the quantum state trajectory
    to uncertain parameters.
\end{enumerate}
We apply these techniques to the fluxonium qubit presented in \cite{zhang2020universal}.
We also show that QOC can solve important problems associated with
fluxonium-based qubits: mitigating
depolarization by taking advantage of the $T_{1}$-dependence of the controls
and synchronizing qubits with distinct frequencies
by performing phase gates in arbitrary times.
To mitigate depolarization,
we perform time-optimal control and
employ an efficient depolarization model
for which the computational cost is independent of the
Hilbert space dimension.
Leveraging recent advances in trajectory optimization within the field of robotics, we
solve these optimization problems using ALTRO (Augmented Lagrangian TRajectory Optimizer)
\cite{howell2019altro}, which can enforce constraints on the quantum state trajectory
and control parameters.

This paper is organized as follows.
First, we describe ALTRO in the context of QOC
in Section \ref{sec:background}.
We outline realistic constraints for operating the fluxonium and
define the associated QOC problem in Section \ref{sec:fluxonium}.
Then, we formulate a method for supressing depolarization
in Section \ref{sec:longitude}. Next, we describe three techniques for achieving
robustness to static parameter uncertainties in Section \ref{sec:static}. We
adapt the same techniques to mitigate 1/$f$ flux noise
in Section \ref{sec:stochastic}.

### 2021-01-26 paper/2background.tex
revised based on dave comments

\section{Background \label{sec:background}}
In this section, we
review the QOC problem statement
and reintroduce the ALTRO solver \cite{howell2019altro}.
QOC concerns a vector of time-dependent control parameters $u(t)$
that steer the evolution of a (quantum) state $\ket{\psi(t)}$.
The evolution of the state is governed by the time-dependent
Schr{\"o}dinger equation (TDSE),
\begin{equation}
  i \hbar \frac{d}{dt} \ket{\psi(t)} = H(u(t), t) \ket{\psi(t)}
  \label{eq:tdse}
\end{equation}
The Hamiltonian $H(u(t), t)$ is determined by the quantum system.
The QOC problem is to find the
controls that minimize a functional $J(u(t))$.
To make the problem numerically tractable,
the controls and state are discretized into $N$ knot points (time steps).
In the case of a single state transfer problem, the functional is
the infidelity of the desired final state and the initial state evolved
to the final knot point,
$J(u) = 1 - {\lvert \braket{\psi_{f}}{\psi_{N}(u)} \rvert}^{2}$.
In general, $J(u)$ is a linear combination of cost functions on the state
as well as cost functions on the controls \cite{leung2017speedup}.
Standard QOC solvers compute derivatives of the functional $\nabla_{u} J(u)$,
which are used to implement first-order optimization methods
\cite{machnes2015tunable, khaneja2005optimal, leung2017speedup, goerz2019krotov}.

Alternatively, the QOC problem can be formulated as a trajectory optimization problem 
and solved using a variety of specialized solvers developed by the robotics community
\cite{Schulman13, Tedrake16, Hereid2017FROST, howell2019altro}.
The functional $J(u)$ is divided into its constituent
cost functions at each knot point $\ell_{k}(x_{k}, u_{k})$,
where $k \in \{1, ..., N\}$ denotes the knot point,
$x_{k}$ is the augmented state vector,
and $u_{k}$ is the augmented control vector.
The augmented state includes all variables of interest that are not decision variables.
In the case of QOC, the state is a subset of the
augmented state $\ket{\psi_{k}} \subseteq x_{k}$.
The solver we use does not currently support complex numbers, so we employ the isomorphism
$\mathcal{H}(\mathbb{C}^{n}) \cong \mathcal{H}(\mathbb{R}^{2n})$
given in \cite{leung2017speedup},
\begin{equation}
  H \ket{\psi} \cong \begin{bmatrix} H_{\textrm{re}} & -H_{\textrm{im}}
    \\ H_{\textrm{im}} & H_{\textrm{re}}\end{bmatrix}
  \begin{bmatrix} \ket{\psi}_{\textrm{re}} \\ \ket{\psi}_{\textrm{im}}\end{bmatrix}
  \label{eq:isomorphism}
\end{equation}
The augmented state trajectory obeys the physics of the system if
the dynamics constraint is satisfied
$x_{k + 1} = f(x_{k}, u_{k})$. For QOC, the discrete
dynamics function $f(x_{k}, u_{k})$ propagates the state by
integrating the TDSE \ref{eq:tdse} with Runge-Kutta methods \cite{jorgensen2011numerical}
or exponential integrators \cite{auer2018magnus, berland2005solving, einkemmer2017performance}.

Additional constraints on the augmented states and augmented controls
are encoded in constraint functions.
The constraint functions are put into a form such that, when the constraint is satisfied,
inequality constraint functions obey $g_{k}(x_{k}, u_{k}) \leq 0$ and
equality constraint functions obey $h_{k}(x_{k}, u_{k}) = 0$. The constraint
functions may be vector-valued to encode multiple constraints of each type.
If a constraint function takes a positive value, the
value is called the constraint's violation and
the constraint is said to be active.
The trajectory optimization problem can be stated concisely,
\begin{mini!}[2]
    {x_{1:N},u_{1:N-1}}{\ell_{N}(x_N) + \sum_{k=1}^{N-1} \ell_{k}(x_k,u_k)}{}{} \label{eq:gcostfun}
    \addConstraint{x_{k+1} = f(x_k,u_k)} \label{eq:gdyncon}
    \addConstraint{g_k(x_k,u_k)}{\leq 0} \label{eq:ineqcon}
    \addConstraint{h_k(x_k,u_k)}{=0} \label{eq:eqcon}
\end{mini!}

Many techniques have been proposed for solving \eqref{eq:gcostfun}-\eqref{eq:eqcon}. Standard 
methods include direction collocation \cite{Hargraves87} and differential-dynamic programming
(DDP) \cite{Mayne1966a}. Recent state-of-the-art solvers, such as ALTRO,
have combined principles from both of these approaches. ALTRO uses iLQR
\cite{Li2004a} as the internal solver of an augmented Lagrangian method (ALM)
\cite{lantoine2012hybrid, plancher2017constrained}
and employs a projected Newton method \cite{bertsekas1982projected, rao1998application}
in its final solving stage.

iLQR simulates the augmented state forward
using the discrete dynamics function 
and computes derivatives of the cost functions
to update the augmented controls. This procedure is known as
indirect shooting, and iLQR shares this approach with GOAT \cite{machnes2015tunable},
GRAPE \cite{khaneja2005optimal, leung2017speedup}, and Krotov's method \cite{goerz2019krotov}.
iLQR differs from these solvers
in its update procedure. iLQR computes the locally optimal update for the augmented
controls using a dynamic programming algorithm, and a line search is performed
in the direction of this update to ensure a decrease in the sum of the cost functions.

Indirect shooting solvers such as iLQR are popular
for solving unconstrained trajectory optimization problems \eqref{eq:gcostfun}-\eqref{eq:gdyncon},
but standard implementations have no ability to handle nonlinear equality and inequality
constraints \eqref{eq:ineqcon}-\eqref{eq:eqcon}.
One way to handle constraints is to employ a projected gradient
method \cite{clarkson2010coresets, hauswirth2016projected}.
However, within the indirect shooting framework,
projected gradient methods can
only handle constraints on the augmented controls,
not the augmented states.
Another technique is to promote the constraint functions to cost functions \cite{leung2017speedup}.
A simple implementation of this approach does not garauntee that the constraints
are satisfied, as the solver trades
minimization of the cost functions and constraint functions against each other.
ALM promotes the constraint functions to cost functions, and adaptively
adjusts a Lagrange multiplier estimate for each constraint function to ensure
the constraints are satisfied. ALM considers a decision variable $z \in \R^{s}$ with $s$ given,
a cost function $f(z) : \R^{s} \mapsto \R$, and a constraint function
$c(z) : \R^{s} \mapsto \R^{p}$ encoding $p$ constraints.
For ALTRO, $z$ is the vector concatenation of the augmented states and augmented controls across
all knot points, $f(z)$ is the sum of the trajectory optimization
cost functions \eqref{eq:gcostfun},
and $c(z)$ is the vector concatenation of the trajectory
optimization constraint functions \eqref{eq:ineqcon}-\eqref{eq:eqcon}.
ALM successively solves unconstrained minimization 
problems of the form:
\begin{mini}[2]
    {z} {f(z) + \lambda^T c(z) + \half c(z)^T I_\mu c(z)}{}{}
    \label{opt:alm}
\end{mini}
$\lambda \in \R^p$ is a Lagrange multiplier estimate, and $I_\mu$ is a diagonal matrix
of penalty weights, $\mu \in \R^{p}$, whose magnitudes depend on whether
the corresponding constraint is active or inactive.
After minimizing \eqref{opt:alm} using iLQR,
the Lagrange multiplier estimates are updated according to,
\begin{equation}
  \lambda \gets \lambda + I_\mu c(z)
  \label{eq:almupdate}
\end{equation}
the penalty weight is updated, and the process repeats until convergence.

ALM converges superlinearly, but poor numerical conditioning may lead
to small decreases in the constraint violations near the locally optimal solution
\cite{bertsekas1996constrained}. To address this shortcoming, ALTRO
projects the solution from the ALM solving stage onto the constraint manifold using
a projected Newton method, achieving ultra-low
constraint violations $\sim 1 \cdot 10^{-8}$.
For more information on the details of the ALTRO
solver, see \cite{howell2019altro, Jackson2020altroc}.

As opposed to standard QOC solvers, ALTRO
is able to satisfy constraints
on both the augmented states and the augmented controls to tight tolerances.
This advantage is crucial for this work, where multiple medium-priority cost functions
are minimized subject to many high-priority constraints.

>>>>

\section{Background \label{sec:background}}
In this section, we
review the QOC problem statement
and describe the ALTRO solver \cite{howell2019altro}.
QOC concerns a vector of time-dependent control parameters $u(t)$
that steer the evolution of a (quantum) state $\ket{\psi(t)}$.
The evolution of the state is governed by the time-dependent
Schr{\"o}dinger equation (TDSE),
\begin{equation}
  i \hbar \frac{d}{dt} \ket{\psi(t)} = H(u(t), t) \ket{\psi(t)}.
  \label{eq:tdse}
\end{equation}
The Hamiltonian $H(u(t), t)$ is determined by the quantum system.
The QOC problem is to find the
controls that minimize a functional $J(u(t))$.
To make the problem numerically tractable,
the controls and state are discretized into $N$ knot points (time steps).
In the case of a single state transfer problem, the functional is
the infidelity of the desired final state and the initial state evolved
to the final knot point,
$J(u) = 1 - {\lvert \braket{\psi_{f}}{\psi_{N}(u)} \rvert}^{2}$.
In general, $J(u)$ is a linear combination of cost functions on the state
as well as cost functions on the controls.
Standard QOC solvers compute derivatives of the functional $\nabla_{u} J(u)$,
which can easily be used to implement first-order optimization methods
\cite{machnes2015tunable, khaneja2005optimal, leung2017speedup, goerz2019krotov}.

Alternatively, the QOC problem can be formulated as a trajectory optimization problem 
and solved using a variety of specialized solvers developed by the robotics community
\cite{Schulman13, Tedrake16, Hereid2017FROST, howell2019altro}.
The functional $J(u)$ is divided into its constituent
cost functions at each knot point $\ell_{k}(x_{k}, u_{k})$,
where $k \in \{1, ..., N\}$ denotes the knot point,
$x_{k}$ is the augmented state vector,
and $u_{k}$ is the augmented control vector.
The augmented state contains all relevant variables
that are dependent upon the controls, for example the state
$\ket{\psi_{k}} \subseteq x_{k}$.
The augmented state trajectory obeys the physics of the system if
the dynamics constraint is satisfied
$x_{k + 1} = f(x_{k}, u_{k})$. For QOC, the discrete
dynamics function $f(x_{k}, u_{k})$ propagates the state by
integrating the TDSE \ref{eq:tdse} with Runge-Kutta methods \cite{jorgensen2011numerical}
or exponential integrators \cite{auer2018magnus, berland2005solving, einkemmer2017performance,
shillito2020fast}.

Additional constraints on the augmented controls and augmented states
are encoded in constraint functions.
The constraint functions are put into a form such that, when the constraint is satisfied,
inequality constraint functions obey $g_{k}(x_{k}, u_{k}) \leq 0$ and
equality constraint functions obey $h_{k}(x_{k}, u_{k}) = 0$. The constraint
functions may be vector-valued to encode multiple constraints of each type.
If a constraint function takes a positive value, the
value is called the constraint's violation.
The trajectory optimization problem can be stated concisely,
\begin{mini!}[2]
    {x_{1:N},u_{1:N-1}}{\ell_{N}(x_N) + \sum_{k=1}^{N-1} \ell_{k}(x_k,u_k)}{}{} \label{eq:gcostfun}
    \addConstraint{x_{k+1} = f(x_k,u_k)} \label{eq:gdyncon}
    \addConstraint{g_k(x_k,u_k)}{\leq 0} \label{eq:ineqcon}
    \addConstraint{h_k(x_k,u_k)}{=0} \label{eq:eqcon}.
\end{mini!}

Standard techniques for solving \eqref{eq:gcostfun}-\eqref{eq:eqcon} typically
fall into two categories: direct methods \cite{Hargraves87, kelly2017introduction}
and indirect methods \cite{betts1998survey}. For indirect methods,
the augmented controls are the decision variables--the
variables the optimizer adjusts to solve the problem.
The augmented states are obtained from the augmented controls using the discrete dynamics function,
and are then used to evaluate derivatives of the cost functions \eqref{eq:gcostfun}.
Then, the derivative information is employed to update the augmented controls.
This is the approach taken by standard QOC solvers such as GOAT \cite{machnes2015tunable},
GRAPE \cite{khaneja2005optimal, leung2017speedup}, and Krotov's method \cite{goerz2019krotov}.
Conversely, direct methods treat both the augmented controls and the augmented states as decision
variables. In addition to minimizing the cost functions, the optimizer uses derivative information
for the discrete dynamics function
to satisfy the dynamics constraint \eqref{eq:gdyncon} to a specified tolerance.
In this sense, the TDSE \eqref{eq:tdse} is a constraint which may be violated
for intermediate steps of the optimization, where the states need not be physical.
The direct approach lends itself to a nonlinear program formulation, for which
a variety of general purpose solvers exist \cite{gill2005snopt, wachter2006implementation}.
Recent state-of-the-art solvers, such as ALTRO,
have combined principles from both of these approaches. ALTRO uses an
iterative linear-quadratic regulator (iLQR) algorithm
\cite{Li2004a} as the internal solver of an augmented Lagrangian method (ALM)
\cite{lantoine2012hybrid, plancher2017constrained}
and employs a projected Newton method \cite{bertsekas1982projected, rao1998application}
in its final solving stage.

iLQR is an indirect method
for solving the dynamically constrained
trajectory optimization problem \eqref{eq:gcostfun}-\eqref{eq:gdyncon},
and its update procedure is based on the differential-dynamic-programming approach
\cite{mayne1966a}.
First, iLQR uses an initial guess for the augmented controls to obtain the augmented
states with the discrete dynamics function.
iLQR then constructs quadratic models for each cost function using
their zeroth-, first- and second-order derivatvies in a Taylor expansion
about the current augmented controls and augmented states.
These models are used to derive a recurrence relation between knot points
which gives the locally optimal update for the augmented controls.
Finally, a line search \cite{zhang2006global}
is performed in the direction of this update to ensure a
decrease in the sum of the cost functions. This procedure
is repeated until convergence.

Indirect solvers such as iLQR are popular
because they are very computationally efficient and maintain
high accuracy for the discrete dynamics throughout optimization.
However, standard implementations have no ability to handle
nonlinear equality and inequality
constraints \eqref{eq:ineqcon}-\eqref{eq:eqcon}.
Projected gradient methods are a typical approach
to handle constraints
\cite{clarkson2010coresets, hauswirth2016projected, morzhin2019minimal,
  nikolskii2007convergence}. Unfortunately, within the indirect framework,
they can only be used for constraints on the augmented controls,
not the augmented states.
Another technique, which is popular for QOC \cite{leung2017speedup},
is to add the constraint functions to the objective
\eqref{eq:gcostfun}. 
This strategy does not guarantee that the constraints
are satisfied as the solver trades
minimization of the cost functions and constraint functions against each other.
ALM remedies this issue by adaptively adjusting a Lagrange multiplier estimate
for each constraint function to ensure the constraints are satisfied.
ALM adds terms that are linear and quadratic in the constraint functions
to the objective. The new objective is then minimized with
iLQR. If the solution produced by iLQR does not satisfy the constraints,
the prefactors for the constraint terms in the objective are increased
and the procedure is repeated.

ALM converges superlinearly, but poor numerical conditioning may lead
to small decreases in the constraint violations near the locally optimal solution
\cite{bertsekas1996constrained}.
To address this shortcoming, ALTRO
projects the solution from the ALM stage onto the constraint manifold using
a projected Newton method, achieving ultra-low
constraint violations $\sim 10^{-8}$.
For more information on the details of the ALTRO
solver, see \cite{howell2019altro, Jackson2020altroc}.

As opposed to standard QOC solvers, ALTRO
can satisfy constraints
on both the augmented controls and the augmented states to tight tolerances.
This advantage is crucial for this work, where multiple medium-priority cost functions
are minimized subject to many high-priority constraints.
